\setlength\headsep{10pt}
\section{Case [insert number]}

%[General description of the case and its evidence] 
 
Sample text:

SUBJECT owned a roofing company. SUBJECT gave his laptop computer to an employee to take to Mom \& Pop's Computer Repair for monitor problems. Upon repairing the laptop, Mom of Mom \& Pop‘s started the laptop to ensure the monitor had been fixed. A standard procedure of Mom \& Pop‘s was to go to the Recent menu on the Start Bar of Windows® 98 systems and select files for viewing. Mom was presented with what appeared to be an image of a young child depicted in a sexually explicit manner. Mom telephoned the county sheriff. A sheriff's deputy responded and observed the image and confirmed it to be a violation of a State statute. The laptop was seized because it contained contraband. The seizure was performed in a manner consistent with recommendations found in Electronic Crime Scene Investigation: A Guide for First Responders. The laptop was entered into evidence according to agency policy, and a search warrant was obtained for the examination of the computer. The computer was submitted for examination. 

%Fill in the following fields you find necessary, and/or have information about, for the case in question:

\begin{longtable}{p{0.5\textwidth}p{0.5\textwidth}}
\textbf{Objective} & [objective of forensics investigation]\\
&\\
\textbf{Computer Type} & [if known/needed]\\
&\\
\textbf{Operating System} & [if known/needed]\\
&\\
\textbf{Offense} & [if known/needed]\\
%&\\
\textbf{Case Agent} & [if known/needed]\\
&\\
\textbf{Evidence Number} &  \#1234567\\
&\\
\textbf{Where examination took place} &  [location] \\
&\\
\textbf{Tools used:} & [specify which tools were used]  
\end{longtable}

\newpage