%Well done! Now that we have the internal document in place we need to make a brief report that the attorney and other non-technical colleagues can get read through swiftly. The brief report below, is an example of a forensics investigation report which contains the essentials of a forensics investigation. This brief version of the report contains all necessary information about the case and, needless to say, it maintains the chain of custody. The italic text is sample text from the source template. When writing your own report, italics should not be used for these sections below.

\section{Case 1 Brief Report}

%Provide the steps used to perform the investigation. This section will vary according to the type of investigation. Add sections as needed.

\begin{longtable}{p{0.5\textwidth}p{0.5\textwidth}}
\textbf{REPORT OF} & Requested Windows Forensic Investigation\\
&\\
\textbf{MEMORANDUM FOR} & \textit{The Super Secret Police} \\
			& \textit{Investigators Fluch \& Bäckström} \\
   & \textit{Super Secret police location (Cloud)}\\
&\\
\textbf{SUBJECT} & \textit{Forensic Media Analysis Report}\\
& \textit{SUBJECT: Gachev, Evgeny}\\
& Case Number: 1\\
\end{longtable}

\begin{enumerate}
\item \textbf{Status: Pending}\\
\item \textbf{System Related Questions}
	\begin{itemize}
	\item REQUESTER provided the following hash sums:
		\begin{itemize}
			\item e6dc38a4f42910729669990138f86265  evgeny\textunderscore 40GB\textunderscore2.raw
			\item fc4fa4b0a97c5f080c48d103cb2dfa64734bb935 evgeny\textunderscore 40GB\textunderscore2.raw
		\end{itemize}
	\item Verfication of the file were confirmed on 2017.10.12 by matching the hash sums provided by REQUESTER.
	\item \textbf{The following findings are all reported by Encase}
		\begin{itemize}
		\item The drive contained 88162304 Total sectors of 512 Bytes per sector 
			and had a total size of 45139095552 Bytes
		\item One partition was found with NTFS as file system with 8 sectors per cluster with a size
			of 512 bytes per sector resulting in a total size of 4096 bytes per cluster.
			Allocated space was 36690026496 bytes (34,2GB) and Unallocated space
			was 8449069056 (7,9GB)
			
			\item The registry hives containing SOFTWARE keys was copied from 
			\begin{itemize}
			
				\item \textbackslash Windows\textbackslash System32\textbackslash config\textbackslash software\\
				
			\end{itemize}
	
		\item Withing the 'software' registry hive, the following information about the operating system was found: The version was Windows 7 professional. Date of installation was Wednesday the 15th pf July 2015, 10:35:41.
		
		
		\end{itemize}
	
\end{itemize}


\item \textbf{Summary of Findings:}\\
Findings in this paragraph are related to Image File: evgeny\textunderscore 40GB\textunderscore 2.raw

	\item The registry hives containing REGISTRY keys was copied from 
	\begin{itemize}
		\item \textbackslash Windows\textbackslash System32\textbackslash config\textbackslash system\\ 
		\item \textbackslash Windows\textbackslash System32\textbackslash config\textbackslash software\\
		\item \textbackslash Windows\textbackslash System32\textbackslash config\textbackslash security\\
		\item \textbackslash Windows\textbackslash System32\textbackslash config\textbackslash sam \\
		\item \textbackslash Windows\textbackslash System32\textbackslash config\textbackslash default \\
		\item \textbackslash Windows\textbackslash System32\textbackslash config\textbackslash system \\
		\item \textbackslash Users\textbackslash evgeny\textbackslash ntuser.dat \\
		Beside 'ntuser.dat' two log files named 'ntuser.dat.LOG1' and 'ntuser.dat.LOG2' were found and copied
		
		\item Withing the 'software' registry hive, under 
		Microsoft \textbackslash Windows \textbackslash CurrentVersion \textbackslash Run, the following information was found about programs that were configured to startup with the system.
		
		\begin{itemize}
			\item "C:\textbackslash Program Files \textbackslash Eraser.exe - atRestart".\\ This is a program designed to remove files on startup.
		\end{itemize}
		
		\item The system is most probably a physical system.
		
		
		
		
	\end{itemize}

\item \textbf{Case Specific Questions}

	\begin{itemize}
		
		\item Looking through the folder \textbackslash Users\textbackslash  within Encase, we found user accounts 
		
		\begin{itemize}
			\item 'Evgeny'
			\item 'Public'
			\item 'Default'
		\end{itemize} 
		
		\item Looking through the registry hive SAM with Registry Viewer, under
		\textbackslash SAM \textbackslash Domains \textbackslash Account \textbackslash Users \textbackslash Names \textbackslash
		 we confirmed these user accounts.
		
		\begin{itemize}
			\item 'Evgeny'
			\item 'Guest'
			\item 'Administrator'
		\end{itemize}
		
		\item within the SAM registry hive, information was found about the login dates.\\ 
		Under \textbackslash SAM \textbackslash Domains \textbackslash Account \textbackslash Users \textbackslash Names \textbackslash evgeny, it was confirmed that the Hexadecimal value for the user (RID value) was 03E8. under
		\textbackslash SAM \textbackslash Domains \textbackslash Account \textbackslash Users \textbackslash 000003E8 \textbackslash the following was found:
		
		\begin{itemize}
		\item User name: 'Evgeny'
		\item Last logon time: 11/6/2015 13:48:51 UTC
		\item Last password change time 7/15/2015 10:35:34 UTC.\\
		If Evgeny hasn't changed his password, this corresponds to the account creation time.
		\item Logon count: 33
		\item User password hint: "NoSuchThingBaby"
		\end{itemize}
		
		\item The installed programs that were found in:
		\textbackslash Program Files \textbackslash \\
		\textbackslash Program Files (x86) \\
		were:
		
		\begin{itemize}
			\item 
			\item 
			\item 
		\end{itemize}
		
		\item email address found evgeny.luckyone@mail.ru
		
		\item hiberfil.sys and pagefile.sys were copied using Encase and searched through
		
	\end{itemize}

\item \textbf{Items Analyzed}

\begin{longtable}{p{0.4\textwidth}p{0.6\textwidth}}
\textbf{\underline{TAG NUMBER}} & \textbf{\underline{ITEM DESCRIPTION}} \\
012345 & One Generic laptop, Serial \#12345677
\end{longtable}

\item \textbf{Details of Findings}

\end{enumerate}

\noindent \textit{IMA D. EXAMINER}	\hfill Released by {\wesa Mr. X}\\
\textit{N.N} Computer Forensic Examiner
\clearpage
